---
title: "Performing literature searches with DiscoverNature"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performing literature searches with explore nature}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting Started

To use this package, you will need to first run the following commands:

```{r }
#install.packages('devtools')
#library(devtools)

#install_github("PHP-2560/r-package-blshli")
#library(DiscoverNature)
```
This code should provide access to the database with information to perform a basic search. There are four main categories that can be searched using this database. These are **explore_keywords**, **explore_subject**, **list,topics**, and **explore_paper**


## Using explore_keywords
One of the options to search the database is through keywords
```{r }
#paper.results <- explore_keywords('stem cells')
#paper.results %>%
  #View()
```


## Using explore_paper
Another way to search is by using aspects of the paper
```{r }
#explore_paper(.title = 'Tppp3+', res = paper.results)
```


## Using explore_subject
